---
title: "Back-calculated WA Test"
author: "Tor Kitching"
date: "2024-01-03"
output: html_document
---

```{r libraries, include=FALSE, echo=FALSE, message=FALSE}
library(rsample)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(gridExtra)
library(reshape2)
library(TMB)
library(zoo)
library(viridis)
library(hrbrthemes)
library(gsl)
library(knitr)
# library(kableExtra)
```

```{r source files, include=FALSE, echo=FALSE, message=FALSE}
source (here::here("R/helperFunctions.R"))
source(here::here("R/PlotFunctions.R"))
source(here::here("R/IWAM_model.R"))
```

## Check for Back-Calculated Watershed Areas

The purpose of this document is to test the back-calculated watershed areas. All code will be drawn from the IWAM function vignette.

## S1. Data Map

The following function vignette/example is from the IWAM Package Repo hosted publicly through the Pacific Salmon Assess organization available at [this link.](https://github.com/Pacific-salmon-assess/iwam-package)

The package currently utilizes the following data sets:

-   *SRinputfile (Private)*: Private data-sets developed by Parken et al. (2006). Required to run the complete function and is available upon request. To be updated with publicly available data. Life histories are included: 1 = ocean type, 0 = stream type. Contains stock names, year, spawners, recruits, and life history identification. 
-   *WatershedArea (Public)*: Internal input containing watershed areas per stock.
-   *CUPars_nBC (Public)*: Input file with Ricker $\alpha$'s without bias correction (CITATION) from Diana Dobson's Run Reconstruction coded in TMB. Has a higher estimate of Ricker $\alpha$ (lower Sgen).
-   *CUPars_wBC (Public)*: Input file with Ricker $\alpha$'s with bias correction (CITATION) from Diana Dobson's Run Reconstruction coded in TMB. Has a higher estimate of Ricker $\alpha$ (lower Sgen).
-   *WCVIStocks (Public)*: User watershed area input file. Must contain watershed areas, life history identification, enhancement identification, and stock name. Aggregation within the IWAM function can be done with both CU and Inlet scales.

## S2. Initialize function

``` {r iwam function, echo=TRUE, message=FALSE, warning=FALSE, results=FALSE}
IWAM_backcalc <- IWAM_func(WAin = "DataIn/Backcalc_targetstocks.csv", # INPUT Data
                       remove.EnhStocks = FALSE, # Enhancement INPUT
                       run.bootstrap = TRUE, # TRUE/FALSE for running the bootstrap process
                       bs_seed = 1, # change the internal seed for the bootstrap
                       bs_nBS = 10, # change the internal number of trials for the bootstrap
                       plot = FALSE, # print plots to DataOut/
                       est.table = TRUE # store tables - NOT FUNCTIONING
)

# "make: Nothing to be done for 'all' - this means that re-compiling the TMB model is NOT necessary
# "Lengths checked passed." - from an internal function test for lengths after joins
```

## S3. Check outputs

This code is a direct lift from the IWAM function vignette. 

Once the model and bootstrapping has completed, the function will store the following objects:

- ```dfout```: A complete data frame containing the SGEN, SREP, and SMSY estimates for each stock and their upper and lower quantiles.
- ```SREP```: A subset of only SREP estimates for a comparative subset of WCVI stocks.
- ```SGEN```: A subset of only SGEN estimates for a comparative subset of WCVI stocks.
- ```SMSY```: A subset of only SMSY estimates for a comparative subset of WCVI stocks.
- ```TBD```: ...

The following tables (1-3) have been prepared for comparison to Holt et al. (2023) (Table 9).

```{r example summary, include=FALSE}
# Bootstrap ouputs e.g. Table 9 in Case Study 2 Page 53:
  # Benchmarks and approximate 95% confidence limits for five inlets, not enhanced
# Paper Shows: Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino
  # Re-work df for only those locations
  # Re-name lwr and upr to be more accurate to their calculation
  # Divide them into different tables by SGEN, SREP, and SMSY
  # Re-name Value to the given esimate name per table
  # Output the tables
locations <- c('Barkley' , 'Clayoquot' , 'Kyuquot' , 'Quatsino' , 'Nootka/Esperanza')
```

```{r SREP, echo=FALSE, message=FALSE}
SREP <- IWAM_backcalc[[2]] %>%
  filter(RP=='SREP') %>%
  filter(Stock %in% locations) %>%
  rename('Lower Quantile'=lwr, 'SREP'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)

kable(SREP)
```

*Table 1. SREP estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*

```{r SGEN, echo=FALSE, message=FALSE}
# kable(IWAM_WCVI[[3]])

SGEN <- IWAM_backcalc[[2]] %>%
  filter(RP=='SGEN') %>%
  filter(Stock %in% locations) %>%
  rename('Lower Quantile'=lwr, 'SGEN'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)

kable(SGEN)
```

*Table 2. SGEN estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*

```{r SMSY, echo=FALSE, message=FALSE}
# kable(IWAM_WCVI[[4]])

SMSY <- IWAM_backcalc[[2]] %>%
  filter(RP=='SMSY') %>%
  filter(Stock %in% locations) %>%
  rename('Lower Quantile'=lwr, 'SMSY'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)

kable(SMSY)
```
*Table 3. SMSY Estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*