---
title: "Back-calculated WA Test"
author: "Tor Kitching"
date: "2024-01-03"
output: html_document
---

```{r libraries, include=FALSE, echo=FALSE, message=FALSE}
library(rsample)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(gridExtra)
library(reshape2)
library(TMB)
library(zoo)
library(viridis)
library(hrbrthemes)
library(gsl)
library(knitr)
```

```{r source files, include=FALSE, echo=FALSE, message=FALSE}
source (here::here("R/helperFunctions.R"))
source(here::here("R/PlotFunctions.R"))
source(here::here("R/IWAM_model.R"))
```

## Check for Back-Calculated Watershed Areas

The purpose of this document is to test the back-calculated watershed areas. All code will be drawn from the IWAM function vignette.

## S1. Data Map

The following function vignette/example is from the IWAM Package Repo hosted publicly through the Pacific Salmon Assess organization available at [this link.](https://github.com/Pacific-salmon-assess/iwam-package)

The package currently utilizes the following data sets:

-   *SRinputfile (Private)*: Private data-sets developed by Parken et al. (2006). Required to run the complete function and is available upon request. To be updated with publicly available data. Life histories are included: 1 = ocean type, 0 = stream type. Contains stock names, year, spawners, recruits, and life history identification. 
-   *WatershedArea (Public)*: Internal input containing watershed areas per stock.
-   *CUPars_nBC (Public)*: Input file with Ricker $\alpha$'s without bias correction (CITATION) from Diana Dobson's Run Reconstruction coded in TMB. Has a higher estimate of Ricker $\alpha$ (lower Sgen).
-   *CUPars_wBC (Public)*: Input file with Ricker $\alpha$'s with bias correction (CITATION) from Diana Dobson's Run Reconstruction coded in TMB. Has a higher estimate of Ricker $\alpha$ (lower Sgen).
-   *Backcalc_targetstocks (Public)*: Back-calculated user watershed area input file. Watershed areas calculated based on Parken estimates of SMSY and SREP. All aggregate information; CU, and Inlet, have been removed. PLEASE NOTE: All WCVI stocks use original watershed areas: Nahmint, Sarita, Somass, Bedwell/Ursus, Cypre, Megin, Moyeha, Tranquil, Artlish, Kaouk, Tahsish, Nitinat, Burman, Conuma, Gold, Leiner, Tahsis, Zeballos, Cayeghle, Marble, San Juan.

## S2. Initialize function

``` {r iwam function, echo=TRUE, message=FALSE, warning=FALSE, results=FALSE}
IWAM_backcalc <- IWAM_func(WAin = "DataIn/Backcalc_targetstocks_NoAgg.csv", # Data (INPUT)
                       remove.EnhStocks = FALSE, # Remove Enhancement stocks (INPUT)
                       run.bootstrap = TRUE, # TRUE/FALSE for running the bootstrap process
                       bs_seed = 1, # Change the internal seed for the bootstrap (INPUT)
                       bs_nBS = 10, # Change the internal number of trials for the bootstrap (INPUT)
                       plot = FALSE, # Print plots to DataOut/
                       est.table = FALSE # Store tables
)
```

## S3. Check outputs

This code is a direct lift from the IWAM function vignette. 

Once the model and bootstrapping has completed, the function will store the following objects:

- ```dfout```: A complete data frame containing the SGEN, SREP, and SMSY estimates for each stock and their upper and lower quantiles.

The following tables (1-3) have been prepared for comparison to Holt et al. (2023) (Table 9).

```{r Complete table, echo=FALSE, message=FALSE}
SREP <- IWAM_backcalc[[2]] %>%
  filter(RP=='SREP') %>%
  rename('Lower Quantile'=lwr, 'SREP'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)
SMSY <- IWAM_backcalc[[2]] %>%
  filter(RP=='SMSY') %>%
  rename('Lower Quantile'=lwr, 'SMSY'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)
SGEN <- IWAM_backcalc[[2]] %>%
  filter(RP=='SGEN') %>%
  rename('Lower Quantile'=lwr, 'SGEN'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)
```

``` {r kabel table, echo=FALSE, message=FALSE}
complete <- data.frame(SGEN, SREP, SMSY) %>% 
  select(-Stock.1, -Stock.2) %>% 
  rename("SGEN LQ" = Lower.Quantile, "SGEN UQ" = Upper.Quantile, "SREP LQ" = Lower.Quantile.1, "SREP UQ" = Upper.Quantile.1, 
         "SMSY LQ" = Lower.Quantile.2, "SMSY UQ" = Upper.Quantile.2)

kable(complete, caption = "SGEN, SREP, and SMSY Estimates for All Stocks")
```
*Table 1. SGEN, SREP, and SMSY estimates including 0.25% and 97.5% quantiles for all listed stocks. Watershed areas are back-calculated from Parken estimates with the exception of WCVI stocks.*

```{r example summary, include=FALSE, eval=FALSE}
# Bootstrap ouputs e.g. Table 9 in Case Study 2 Page 53:
  # Benchmarks and approximate 95% confidence limits for five inlets, not enhanced
# Paper Shows: Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino
  # Re-work df for only those locations
  # Re-name lwr and upr to be more accurate to their calculation
  # Divide them into different tables by SGEN, SREP, and SMSY
  # Re-name Value to the given esimate name per table
  # Output the tables
locations <- c('Barkley' , 'Clayoquot' , 'Kyuquot' , 'Quatsino' , 'Nootka/Esperanza')
```

```{r SREP, echo=FALSE, message=FALSE, eval=FALSE}
SREP <- IWAM_backcalc[[2]] %>%
  filter(RP=='SREP') %>%
  # filter(Stock %in% locations) %>%
  rename('Lower Quantile'=lwr, 'SREP'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)

kable(SREP)
# *Table 1. SREP estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*
```

```{r SGEN, echo=FALSE, message=FALSE, eval=FALSE}
# kable(IWAM_WCVI[[3]])

SGEN <- IWAM_backcalc[[2]] %>%
  filter(RP=='SGEN') %>%
  # filter(Stock %in% locations) %>%
  rename('Lower Quantile'=lwr, 'SGEN'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)

kable(SGEN)
# *Table 2. SGEN estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*
```

```{r SMSY, echo=FALSE, message=FALSE, eval=FALSE}
# kable(IWAM_WCVI[[4]])

SMSY <- IWAM_backcalc[[2]] %>%
  filter(RP=='SMSY') %>%
  # filter(Stock %in% locations) %>%
  rename('Lower Quantile'=lwr, 'SMSY'=Value, 'Upper Quantile'=upr) %>%
  mutate(RP = NULL) %>%
  relocate(Stock)

kable(SMSY)
# *Table 3. SMSY Estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*
```