---
title: "IWAM Function Vignette"
output: html_document
date: "2023-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE, echo=FALSE, message=FALSE}
library(rsample)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(gridExtra)
library(reshape2)
library(TMB)
library(zoo)
library(viridis)
library(hrbrthemes)
library(gsl)
library(knitr)
# library(kableExtra)
```

### Source Files

```{r source files, include=FALSE, echo=FALSE, message=FALSE}
source (here::here("R/helperFunctions.R"))
source(here::here("R/PlotFunctions.R"))
source(here::here("R/IWAM_model.R")) # Will itself source the bootstrap code through the function Get.LRP.bs()
```


# IWAM Function Vignette

Authors: Carrie Holt (1), Kendra Holt (1), and Brooke Davis (1)

(1) Department of Fisheries and Oceans (DFO), Canada

## Document Contents

1.  Summary
2.  Data Map
3.  Function
4.  Outputs

## S1. Summary

The purpose of the IWAM function is to provide estimates for SREP, SGEN, and SMSY, using habitat-based assessments methods (the Integrated Watershed Area model) in a streamlined process. This function is based upon the work of (insert history). This function is maintained by Carrie Holt (1) and Tor Kitching (1).

(1) Department of Fisheries and Oceans (DFO), Canada

## S2. Data Map

The following function vignette/example is from the IWAM Package Repo hosted publicly through the Pacific Salmon Assess organization available at [this link.](https://github.com/Pacific-salmon-assess/iwam-package)

The package currently utilizes the following data sets:

-   *SRinputfile (Private)*: Private data-sets developed by Parken et al. (2006). Required to run the complete function and is available upon request. To be updated with publicly available data. Life histories are included: 1 = ocean type, 0 = stream type. Contains stock names, year, spawners, recruits, and life history identification. 
-   *WatershedArea (Public)*: Internal input containing watershed areas per stock.
-   *CUPars_nBC (Public)*: Input file with Ricker $\alpha$'s without bias correction (CITATION) from Diana Dobson's Run Reconstruction coded in TMB. Has a higher estimate of Ricker $\alpha$ (lower Sgen).
-   *CUPars_wBC (Public)*: Input file with Ricker $\alpha$'s with bias correction (CITATION) from Diana Dobson's Run Reconstruction coded in TMB. Has a higher estimate of Ricker $\alpha$ (lower Sgen).
-   *WCVIStocks (Public)*: User watershed area input file. Must contain watershed areas, life history identification, enhancement identification, and stock name. Aggregation within the IWAM function can be done with both CU and Inlet scales.

## S3. Function Run Example

The IWAM function is defined by two sets of parameters, the inputs;

-  ```WAin```: a string containing the file path to your watershed area data.
-  ```remove.EnhStocks```: a TRUE/FALSE statement of whether or not to remove enhanced stock populations from analysis.

and the run specifications;

-  ```run.bootstrap```: a TRUE/FALSE statement of whether to run the bootstrapping internal process.
-  ```bs_seed```: a NUMERIC value for your desired bootstrapping seed.
-  ```bs_nBS```: a NUMERIC value for your desired number of trials.
-  ```plot```: a TRUE/FALSE statement of whether to print out plots to your DataOut folder.
-  ```est.table```: a TRUE/FALSE statement of whether to store final SREP, SGEN, and SMSY tables. Please see Section 4 for examples.

The IWAM function is divided into two major sections. 

1. The IWAM model; which estimates SREP and SMSY. This model is based upon the work of Parken et al. 2006 and Liermann et al. as a modification to the Ricker model.
2. Model bootstrapping; which takes the estimates of the IWAM model and runs them through an iterative bootstrap to re-estimate SREP, SMSY, and SGEN based on an updated set of priors (CITATION).

``` {r iwam function, echo=TRUE, message=FALSE, warning=FALSE, results=FALSE}
IWAM_WCVI <- IWAM_func(WAin = "DataIn/WCVIStocks.csv", # INPUT Data
                       remove.EnhStocks = TRUE, # Enhancement INPUT
                       run.bootstrap = TRUE, # TRUE/FALSE for running the bootstrap process
                       bs_seed = 1, # change the internal seed for the bootstrap
                       bs_nBS = 10, # change the internal number of trials for the bootstrap
                       plot = FALSE, # print plots to DataOut/
                       est.table = TRUE # store tables - NOT FUNCTIONING
)

# "make: Nothing to be done for 'all' - where is this error coming from?
# "Lengths checked passed." - from an internal function test for lengths after joins

```
``` {r iwam function dummy data, echo=TRUE, message=FALSE, warning=FALSE, results=FALSE}
# This is a test function run on dummy data with NO AGGREGATIONS
IWAM_NoInlet <- IWAM_func(WAin = "DataIn/WCVIStocks_NoInlet.csv", # INPUT Data
                          remove.EnhStocks = TRUE, # Enhancement INPUT
                          run.bootstrap = TRUE, # TRUE/FALSE for running the bootstrap process
                          bs_seed = 1, # change the internal seed for the bootstrap
                          bs_nBS = 10, # change the internal number of trials for the bootstrap
                          plot = FALSE, # print plots to DataOut/
                          est.table = TRUE # store tables - NOT FUNCTIONING
)
```

``` {r iwam function dummy data 2, echo=TRUE, message=FALSE, warning=FALSE, results=FALSE}
# This is a test function run on dummy data with NO AGGREGATIONS
IWAM_NoAgg <- IWAM_func(WAin = "DataIn/WCVIStocks_NoAgg.csv", # INPUT Data
                        remove.EnhStocks = TRUE, # Enhancement INPUT
                        run.bootstrap = TRUE, # TRUE/FALSE for running the bootstrap process
                        bs_seed = 1, # change the internal seed for the bootstrap
                        bs_nBS = 10, # change the internal number of trials for the bootstrap
                        plot = FALSE, # print plots to DataOut/
                        est.table = TRUE # store tables - NOT FUNCTIONING
)
```

## S4. Outputs Example

Once the model and bootstrapping has completed, the function will store the following objects:

- ```dfout```: A complete data frame containing the SGEN, SREP, and SMSY estimates for each stock and their upper and lower quantiles.
- ```SREP```: A subset of only SREP estimates for a comparative subset of WCVI stocks.
- ```SGEN```: A subset of only SGEN estimates for a comparative subset of WCVI stocks.
- ```SMSY```: A subset of only SMSY estimates for a comparative subset of WCVI stocks.
- ```TBD```: ...

The following tables (1-3) have been prepared for comparison to Holt et al. (2023) (Table 9).

```{r example summary, include=FALSE}
# Bootstrap ouputs e.g. Table 9 in Case Study 2 Page 53:
  # Benchmarks and approximate 95% confidence limits for five inlets, not enhanced
# Paper Shows: Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino
  # Re-work df for only those locations
  # Re-name lwr and upr to be more accurate to their calculation
  # Divide them into different tables by SGEN, SREP, and SMSY
  # Re-name Value to the given esimate name per table
  # Output the tables
locations <- c('Barkley' , 'Clayoquot' , 'Kyuquot' , 'Quatsino' , 'Nootka/Esperanza')
```

```{r SREP, echo=FALSE, message=FALSE}
SREP <- IWAM_WCVI[[3]] %>% # Already SREP
  # filter(RP=='SREP') %>%
  filter(Stock %in% locations) # %>%
  # rename('Lower Quantile'=lwr, 'SREP'=Value, 'Upper Quantile'=upr) %>%
  # mutate(RP = NULL) %>%
  # relocate(Stock)

kable(SREP)
```

*Table 1. SREP estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*

```{r SGEN, echo=FALSE, message=FALSE}
# kable(IWAM_WCVI[[3]])

SGEN <- IWAM_WCVI[[4]] %>%
  # filter(RP=='SGEN') %>%
  filter(Stock %in% locations) # %>%
  # rename('Lower Quantile'=lwr, 'SGEN'=Value, 'Upper Quantile'=upr) %>%
  # mutate(RP = NULL) %>%
  # relocate(Stock)

kable(SGEN)
```

*Table 2. SGEN estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*

```{r SMSY, echo=FALSE, message=FALSE}
# kable(IWAM_WCVI[[4]])

SMSY <- IWAM_WCVI[[5]] %>%
  # filter(RP=='SMSY') %>%
  filter(Stock %in% locations) # %>%
  # rename('Lower Quantile'=lwr, 'SMSY'=Value, 'Upper Quantile'=upr) %>%
  # mutate(RP = NULL) %>%
  # relocate(Stock)

kable(SMSY)
```
*Table 3. SMSY Estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*