---
title: "IWAM Function Vignette"
output: html_document
date: "2023-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE, echo=FALSE, message=FALSE}
library(rsample)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(gridExtra)
library(reshape2)
library(TMB)
library(zoo)
library(viridis)
library(hrbrthemes)
library(gsl)
library(knitr)
# library(kableExtra)
```

### Source Files

```{r source files, include=FALSE, echo=FALSE, message=FALSE}
source (here::here("R/helperFunctions.R"))
source(here::here("R/PlotFunctions.R"))
# source(here::here("R/WCVILRPs_bootstrap.R")) # Not used anymore directly
source(here::here("R/IWAM_model.R")) # Will itself source the bootstrap code through the function Get.LRP.bs()
```


# IWAM Function Vignette

Authors: Carrie Holt (1)

(1) Department of Fisheries and Oceans (DFO), Canada

## Document Contents

1.  Summary (Function Inputs and Outputs)
2.  Data Map
3.  Function Run Example
4.  Outputs

## S1. Summary

The purpose of the IWAM function is to provide estimates for SREP, SGEN, and SMSY, using habitat-based assessments methods (the Integrated Watershed Area model) in a streamlined process. This function is based upon the work of (insert history). This function is maintained by (insert authors).

## S2. Data Map

The following function vignette/example is from the IWAM Package Repo hosted publicly through the Pacific Salmon Assess organization available at [this link.](https://github.com/Pacific-salmon-assess/iwam-package)

The package currently utilizes the following data sets:

-   CUPars_nBC *\**
-   CUPars_wBC *\**
-   ParkenSMSY *\**
-   ParkenSREP *\**
-   SRinputs *\**
-   Surv *\**
-   WA_Parken *\**
-   WatershedArea *\**
-   WCVIEsc *\**
-   *WCVIStocks (Public)*

(*\**) Currently private, but available upon request. You will require all listed files to run the function.

## S3. Function Run Example

The IWAM function is defined by the following outputs:

-  ```WA```: a string  containing the file path to your watershed area data.
-  ```run.bootstrap```: a TRUE/FALSE statement of whether to run the bootstrapping internal process.
-  ```bs_seed```: a NUMERIC value for your desired bootstrapping seed.
-  ```bs_nBS```: a NUMERIC value for your desired number of trials.
-  ```mod```: the name of your TMB model.
-  ```remove.EnhStocks```: a TRUE/FALSE statement of whether or not to remove enhanced stock populations from analysis.
-  ```plot```: a TRUE/FALSE statement of whether to print out plots to your DataOut folder.
-  ```est.table```: a TRUE/FALSE statement of whether to store final SREP, SGEN, and SMSY tables. Please see Section 4 for examples.

The IWAM function is divided into two major sections. 

1. The IWAM model; which estimates SREP and SMSY. This model is based upon the work of Parken et al. 2006 and Liermann et al. as a modification to the Ricker model.
2. Model bootstrapping; which takes the estimates of the IWAM model and runs them through an iterative bootstrap to re-estimate SREP, SMSY, and SGEN based on an updated set of priors (INSERT CITATION).

``` {r iwam_model, echo=TRUE, message=FALSE, warning=FALSE, results=FALSE}
IWAM_test <- IWAM_func(WA = "DataIn/WatershedArea.csv",
          # datain = "file/path", # reference to outputs of IWAM output - just in case they change (REDUNDANCY)
          run.bootstrap = TRUE, 
          bs_seed = 1, # change the internal seed for the bootstrap from outside
          bs_nBS = 10, # change the internal number of trials for the bootstrap from outside (Original run 20000)
          mod = "IWAM_Liermann", # TMB Mod name
          remove.EnhStocks = TRUE,
          plot = FALSE, # print plots to DataOut/
          est.table = TRUE # store tables # Not functioning
)
```

## S4. Outputs Example

Once the model and bootstrapping has completed, the function will store the following objects:

- ```dfout```: A complete data frame containing the SGEN, SREP, and SMSY estimates for each stock and their upper and lower quantiles.
- ```SREP```: A subset of only SREP estimates for a comparative subset of WCVI stocks.
- ```SGEN```: A subset of only SGEN estimates for a comparative subset of WCVI stocks.
- ```SMSY```: A subset of only SMSY estimates for a comparative subset of WCVI stocks.
- ```TO BE ADDED AS NEEDED```: ...

The following tables (1-3) have been prepared for comparison to Holt et al. (2023) (Table 9).

```{r example summary, include=FALSE}
# Bootstrap ouputs e.g. Table 9 in Case Study 2 Page 53:
  # Benchmarks and approximate 95% confidence limits for five inlets, not enhanced
# Paper Shows: Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino
  # Re-work df for only those locations
  # Re-name lwr and upr to be more accurate to their calculation
  # Divide them into different tables by SGEN, SREP, and SMSY
  # Re-name Value to the given esimate name per table
  # Output the tables
# locations <- c('Barkley' , 'Clayoquot' , 'Kyuquot' , 'Quatsino' , 'Nootka/Esperanza')
```

```{r SREP, echo=FALSE, message=FALSE}
kable(IWAM_test[[2]])

# SREP <- dfout %>%
#   filter(RP=='SREP') %>%
#   filter(Stock %in% locations) %>%
#   rename('Lower Quantile'=lwr, 'SREP'=Value, 'Upper Quantile'=upr) %>%
#   mutate(RP = NULL) %>%
#   relocate(Stock)
# 
# kable(SREP)
```

*Table 1. SREP estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*

```{r SGEN, echo=FALSE, message=FALSE}
kable(IWAM_test[[3]])

# SGEN <- dfout %>%
#   filter(RP=='SGEN') %>%
#   filter(Stock %in% locations) %>%
#   rename('Lower Quantile'=lwr, 'SGEN'=Value, 'Upper Quantile'=upr) %>%
#   mutate(RP = NULL) %>%
#   relocate(Stock)
# 
# kable(SGEN)
```

*Table 2. SGEN estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*

```{r SMSY, echo=FALSE, message=FALSE}
kable(IWAM_test[[4]])

# SMSY <- dfout %>%
#   filter(RP=='SMSY') %>%
#   filter(Stock %in% locations) %>%
#   rename('Lower Quantile'=lwr, 'SMSY'=Value, 'Upper Quantile'=upr) %>%
#   mutate(RP = NULL) %>%
#   relocate(Stock)
# 
# kable(SMSY)
```
*Table 3. SMSY Estimates including 0.25% and 97.5% quantiles for Barkley, Clayoquot, Kyuquot, Nootka/Esperanza, Quatsino.*