---
title: "WCVI Worked Example"
output: pdf_document
date: "2023-11-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE, echo=FALSE}
library(rsample)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(gridExtra)
library(reshape2)
library(TMB)
library(zoo)
library(viridis)
library(hrbrthemes)
library(gsl)
```

```{r source files, include=FALSE, echo=FALSE}
source (here::here("R/helperFunctions.R"))
source(here::here("R/PlotFunctions.R")) 
source(here::here("R/WCVILRPs_bootstrap.R"))
```

# WCVI Worked Example

## Content

- Summary
- Key code repositories, where to find data, etc. ("Data Map")
- Reference to comparison paper: https://publications.gc.ca/collections/collection_2023/mpo-dfo/fs70-5/Fs70-5-2023-010-eng.pdf 
- Link to iwam-package repository
- Preliminary code loading
  - Packages (code chunk)
  - Source functions (code chunk)

## Stage 1
- IWAM_model - produce the initial SREP estimates 
  - Run code internally - what is worth hiding versus not?

```{r iwam-model, include=FALSE}
# IWAM Model Setup
remove.EnhStocks <- TRUE

srdatwna <- read.csv(here::here("DataIn/SRinputfile.csv")) # PRIVATE
WA <- read.csv(here::here("DataIn/WatershedArea.csv")) # PRIVATE
wcvistocks <- read.csv(here::here("DataIn/WCVIStocks.csv"))

srdatwna <- srdatwna %>% filter(Name != "Hoko" & Name != "Hoh") 
stockwna <- srdatwna %>% filter (is.na(Rec) == TRUE) %>% 
  dplyr::select (Stocknumber) %>%  unique() %>% unlist() 
srdat <- srdatwna %>% filter(Rec != "NA") 

if(max(srdat$Stocknumber) >= stockwna[1]) { 
  for (i in 1:length(stockwna)) { 
    len <- length (srdat[which (srdat$Stocknumber == stockwna[i]), ]$yr_num) - 1
    srdat [which (srdat$Stocknumber == stockwna[i]), ]$yr_num <- c (0:len)
  }
}

srdat <- digit_scaling(srdat)
srdat_scale <- srdat %>% dplyr::select(Stocknumber, scale) %>% distinct()
srdat_scale <- srdat_scale$scale 
srdat_cow <- srdat %>% filter(Name == "Cowichan" & 
                                Yr >= 1985 & 
                                Yr !=1986 & 
                                Yr != 1987) # length = 10
n_cow <- length(srdat_cow$Yr)
srdat_cow$yr_num <- 0:(n_cow-1)
srdat <- srdat %>%  filter(Name != "Cowichan") %>% bind_rows(srdat_cow) %>%
  arrange(Stocknumber)

names <- srdat %>% dplyr::select (Stocknumber, Name) %>% distinct()
WA <- WA %>% full_join(names, by="Name") %>% arrange(Stocknumber)
stream <- srdat %>% dplyr::select(Stocknumber, Name, Stream) %>% #srdat Stream is still capcased
  group_by(Stocknumber) %>% 
  summarize(lh=max(Stream)) %>% 
  arrange (Stocknumber)

data <- list()

scale_TMB <- srdat$scale # scale enters the TMB data as: scale
data$S <- srdat$Sp/scale_TMB # Spawners / scale 
data$logRS <- log( (srdat$Rec/srdat$scale) / (srdat$Sp/srdat$scale) )
data$stk <- as.numeric(srdat$Stocknumber) # stock number
data$yr <- srdat$yr_num
N_Stocks <- length(unique(srdat$Name))
data$logMuA_stream_mean <- 1.5 
data$logMuA_stream_sig <- 2
data$logMuA_ocean_mean <- 0 #1.5
data$logMuA_ocean_sig <- 2
data$HalfNormMean <- 0 #TMB_Inputs$Tau_sigma
data$HalfNormSig <- 1 #TMB_Inputs$Tau_sigma
data$HalfNormMeanA <- 0 #0.44 #TMB_Inputs$Tau_sigma
data$HalfNormSigA <- 1 #0.5 #TMB_Inputs$Tau_sigma
data$WA <- WA$WA
data$stream <- stream$lh
data$scale <- srdat_scale # Ordered by Stocknumber
data$SigRicPriorNorm <- as.numeric(F)
data$SigRicPriorGamma <- as.numeric(T)
data$SigRicPriorCauchy <- as.numeric(F)
data$biasCor <- as.numeric(TRUE)
data$SigDeltaPriorNorm <- as.numeric(F)
data$SigDeltaPriorGamma <- as.numeric(T)
data$SigDeltaPriorCauchy <- as.numeric(F)
data$Tau_dist <- 0.1
data$Tau_D_dist <- 1
data$SigDelta_mean <- 0.80 # See KFrun.R, #For half-normal use N(0,1)
data$SigDelta_sig <- 0.28 # See KFrun.R,
data$SigNu_mean <- 0.84 # See KFrun.R,
data$SigNu_sig <- 0.275 # See KFrun.R,

data$pred_lnWA <- seq(min(log(WA$WA)), max(log(WA$WA)), 0.1)

data$target_lnWA_ocean <- wcvistocks %>% # PUBLIC
  mutate (lnWA=log(WA)) %>%
  filter(lh==1) %>% 
  pull(lnWA)

data$target_lnWA_stream <- wcvistocks %>% # PUBLIC
  mutate (lnWA=log(WA)) %>%
  filter(lh==0) %>% # not present in wcvistocks
  pull(lnWA)

InletlnWA <- data.frame(wcvistocks) %>%
  filter(Stock != "Cypre") %>% 
  group_by(Inlet) %>%
  summarize(InletlnWA = log(sum(WA))) %>% 
  filter(Inlet != "San Juan") %>%
  filter(Inlet !="Nitinat")

InletlnWAnoEnh <- data.frame(wcvistocks) %>% 
  filter(Stock != "Cypre") %>% filter(Enh==0) %>%
  group_by(Inlet) %>% 
  summarize(InletlnWA = log(sum(WA))) %>% 
  filter(Inlet != "San Juan") %>%
  filter(Inlet !="Nitinat")

CUlnWA <- data.frame(wcvistocks) %>% 
  filter(Stock != "Cypre") %>% 
  group_by(CU) %>%
  summarize(CUlnWA = log(sum(WA)))

CUlnWAnoEnh <- data.frame(wcvistocks) %>% 
  filter(Stock != "Cypre") %>% 
  filter(Enh==0) %>%
  group_by(CU) %>% 
  summarize(CUlnWA = log(sum(WA)))

if(remove.EnhStocks) data$target_lnWA_ocean <- c(data$target_lnWA_ocean, 
                                         InletlnWAnoEnh$InletlnWA,
                                           CUlnWAnoEnh$CUlnWA)

param <- list()

param$logA <- ( srdat %>% group_by (Stocknumber) %>% 
                      summarise(yi = lm(log( Rec / Sp) ~ Sp )$coef[1] ) )$yi
B <- srdat %>% group_by(Stocknumber) %>% 
  summarise( m = - lm(log( Rec / Sp) ~ Sp )$coef[2] )
param$logB <- log ( 1/ ( (1/B$m)/data$scale ))
param$logSigma <- rep(-2, N_Stocks)
param$logMuA_stream <- 1.5
param$logSigmaA <- -2
param$logMuA_ocean <- 0
param$logDelta1 <- 3 
param$logDelta1_ocean <- 0
param$logDelta2 <- log(0.72) 
param$Delta2_ocean <- 0 
param$logDeltaSigma <- -0.412 
param$logNu1 <- 3
param$logNu1_ocean <- 0
param$logNu2 <- log(0.72)
param$Nu2_ocean <- 0
param$logNuSigma <- -0.412 
```

```{r iwam-model, include=FALSE}
# IWAM Model Run
mod <- "IWAM_Liermann" 
# dyn.unload(dynlib(paste("TMB_Files/", mod, sep="")))
# compile(paste("TMB_Files/", mod, ".cpp", sep=""))
dyn.load(dynlib(here::here(paste("TMB_Files/", mod, sep=""))))

obj <- MakeADFun(data, param, DLL=mod, silent=TRUE, random = c("logA"))

upper <- unlist(obj$par)
upper[1:length(upper)]<- Inf
lower <- unlist(obj$par)
lower[1:length(lower)]<- -Inf

opt <- nlminb(obj$par, 
              obj$fn, 
              obj$gr, 
              control = list(eval.max = 1e5, iter.max = 1e5), 
              lower=lower, 
              upper=upper)

pl <- obj$env$parList(opt$par) 

all_pars <- data.frame(summary(sdreport(obj)))
all_pars$Param <- row.names(all_pars)

all_pars$Param <- sapply(all_pars$Param, function(x) (unlist(strsplit(x, "[.]"))[[1]]))


pars <- data.frame()
pars <- all_pars %>% filter (Param %in% c("logA", 
                                          "logB", 
                                          "logSigma",  
                                          "SMSY", 
                                          "SREP"))

stnum <- unique(srdat[, c("Stocknumber")])
pars$Stocknumber <- rep(stnum)
pars <- left_join(pars, unique(srdat[, c("Stocknumber", "Name")]))

logDeltaSigma <- all_pars %>% filter (Param %in% c("logDeltaSigma")) 
DeltaSigmaUCL <- exp(logDeltaSigma$Estimate + logDeltaSigma$Std..Error*1.96)
DeltaSigmaLCL <- exp(logDeltaSigma$Estimate - logDeltaSigma$Std..Error*1.96) 
DeltaSigma <- exp(logDeltaSigma$Estimate)

pars$Param <- sapply(pars$Param, function(x) (unlist(strsplit(x, "[_]"))[[1]]))
pars <- pars %>% left_join(stream, by="Stocknumber")


all_Deltas <- data.frame()
all_Deltas <- all_pars %>% filter (Param %in% c("logDelta1", 
                                                "logDelta2",
                                                "sigma_delta", 
                                                "Delta2_bounded", 
                                                "logDelta1_ocean", 
                                                "Delta2_ocean", 
                                                "logNu1", 
                                                "logNu2", 
                                                "sigma_nu", 
                                                "logNu1_ocean", 
                                                "Nu2_ocean"))

nLL <- data.frame(nLL=obj$report()$nLL) %>% 
  add_column(Stocknumber=srdat$Stocknumber) %>% group_by(Stocknumber) %>% 
  summarize(CnLL=sum(nLL))
AIC <- nLL %>% mutate(aic = 2 * 3 + 2*CnLL) 

pred_RS <- data.frame()
pred_RS <- all_pars %>% filter (Param %in% c("logRS_pred"))

all_pred <- srdat %>% dplyr::select("Stocknumber",
                                 "yr_num", 
                                 "Sp", 
                                 "Rec", 
                                 "scale", 
                                 "Name") %>% 
  add_column(Pred=pred_RS$Estimate)

if (length(pred_RS$Estimate) == length(data$S)) {
  print("Lengths checked passed.")
} else {
  print("WARNING: The output and inputs are not the same length.")
}

all_pred <- all_pred %>% mutate(ObslogRS = log ( (Rec / scale) / (Sp/scale) ) )
r2 <- all_pred %>% group_by(Stocknumber) %>% summarize(r2=cor(ObslogRS,Pred)^2)

pred_lnSMSY <- data.frame() 
pred_lnSMSY <- all_pars %>% filter (Param %in% c("pred_lnSMSY_stream", 
                                                "pred_lnSMSY_ocean", 
                                                "pred_lnSMSY_CI", 
                                                "pred_lnSMSY_stream_CI", 
                                                "pred_lnSMSY_ocean_CI"))
pred_lnSREP <- data.frame() 
pred_lnSREP <- all_pars %>% filter (Param %in% c("pred_lnSREP_stream", 
                                                "pred_lnSREP_ocean", 
                                                "pred_lnSREP_CI", 
                                                "pred_lnSREP_stream_CI", 
                                                "pred_lnSREP_ocean_CI"))

SRes <- all_pred %>% mutate ( Res = ObslogRS- Pred)
sigma <- pars %>% filter(Param=="logSigma") %>% dplyr::select(Stocknumber, Estimate, Name)
SRes <- SRes %>% left_join(sigma) %>% rename(logSig = Estimate)
SRes <- SRes %>% mutate (StdRes = Res/exp(logSig))
```

```{r iwam plotting, include=FALSE, echo=FALSE}
PlotSRCurve(srdat=srdat, pars=pars, r2=r2, removeSkagit = FALSE, mod=mod)
```

```{r iwam plotting, include=FALSE, echo=FALSE}
PlotSRLinear(srdat=srdat, pars=pars, r2=r2, removeSkagit = FALSE)
```

```{r iwam plotting, include=FALSE, echo=FALSE}
PlotStdResid(SRes)
```

```{r iwam plotting, include=FALSE, echo=FALSE}
Plotacf(SRes)
```

```{r iwam-model, include=FALSE, echo=FALSE}
# echo=FALSE prevents printing the code and just allows for the figure output
# IWAM Model Outputs/Plotting - consider including
# WA regression SMSY
# WA regression SREP
# SR IWAM
# SRLin IWAM
# StdResid IWAM

# Remove looping and make them plot naturally in RMD
# PlotSRCurve(srdat=srdat, pars=pars, r2=r2, removeSkagit = FALSE, mod=mod)
# PlotSRLinear(srdat=srdat, pars=pars, r2=r2, removeSkagit = FALSE)
# PlotStdResid(SRes)
# Plotacf(SRes)

# if (plot==TRUE){
#   png(paste("DataOut/SR_", mod, ".png", sep=""), width=7, height=7, units="in", res=500)
#   PlotSRCurve(srdat=srdat, pars=pars, r2=r2, removeSkagit = FALSE, mod=mod)
#   dev.off()
#   png(paste("DataOut/SRLin_", mod, ".png", sep=""), width=7, height=7, units="in", res=1000)
#   PlotSRLinear(srdat=srdat, pars=pars, r2=r2, removeSkagit = FALSE)
#   dev.off()
#   png(paste("DataOut/StdResid_", mod, ".png", sep=""), width=7, height=7, units="in", res=1000)
#   PlotStdResid(SRes)
#   dev.off()
#   png(paste("DataOut/ACF_", mod, ".png", sep=""), width=7, height=7, units="in", res=1000)
#   Plotacf(SRes)
#   dev.off()
# }

par(mfrow=c(1,1), mar=c(4, 4, 4, 2) + 0.1)
title_plot <- "Prior Ricker sigma and prior WA regression sigma"
plotWAregressionSMSY (pars, all_Deltas, srdat, stream, WA, pred_lnSMSY, 
                        pred_lnWA = data$pred_lnWA, title1=title_plot, mod)
# dev.off()

par(mfrow=c(1,1), mar=c(4, 4, 4, 2) + 0.1)
title_plot <- "Prior Ricker sigmas and prior on WA regression sigma"
plotWAregressionSREP (pars, all_Deltas, srdat, stream, WA, pred_lnSREP, 
                        pred_lnWA = data$pred_lnWA, title1=title_plot, mod)
# dev.off()

# if(plot==TRUE){
#   png(paste("DataOut/WAregSMSY_", mod, "_wBC.png", sep=""), width=7, height=7, units="in", res=500)
#   par(mfrow=c(1,1), mar=c(4, 4, 4, 2) + 0.1)
#   title_plot <- "Prior Ricker sigma and prior WA regression sigma"
#   #title_plot <- "Separate life-histories: n=17\nFixed-effect yi (logDelta1), \nFixed-effect slope (Delta2)"
#   plotWAregressionSMSY (pars, all_Deltas, srdat, stream, WA, pred_lnSMSY, 
#                         pred_lnWA = data$pred_lnWA, title1=title_plot, mod)
#   dev.off()
#   
#   png(paste("DataOut/WAregSREP_", mod, "_wBC.png", sep=""), width=7, height=7, units="in", res=500)
#   #png(paste("DataOut/WAreg_Liermann_SepRicA_UniformSigmaAPrior.png", sep=""), width=7, height=7, units="in", res=500)
#   par(mfrow=c(1,1), mar=c(4, 4, 4, 2) + 0.1)
#   title_plot <- "Prior Ricker sigmas and prior on WA regression sigma"
#   #title_plot <- "Separate life-histories: n=17\nFixed-effect yi (logDelta1), \nFixed-effect slope (Delta2)"
#   plotWAregressionSREP (pars, all_Deltas, srdat, stream, WA, pred_lnSREP, 
#                         pred_lnWA = data$pred_lnWA, title1=title_plot, mod)
#   dev.off()
#   #plotWAregression (pars, all_Deltas, srdat, stream, WA, pred_lnSMSY, pred_lnWA = data$pred_lnWA, 
#   # title1="Common, fixed yi (logDelta1), \nRandom slope (Delta2)")
# }
```

```{r final step, include=FALSE}
pred_lnSMSY_pi <- data.frame()
pred_lnSMSY_pi <- all_pars %>% filter   (Param %in% c("pred_lnSMSY", "lnSMSY"))
pred_lnSREP_pi <- data.frame()
pred_lnSREP_pi <- all_pars %>% filter (Param %in% c("pred_lnSREP", "lnSREP"))

pred_lnSMSY_pi$Stocknumber <- rep(stnum)
pred_lnSREP_pi$Stocknumber <- rep(stnum)

scale_pi <- srdat %>% dplyr::select(Stocknumber, scale) %>% distinct()
pred_lnSMSY_pi <- pred_lnSMSY_pi %>% left_join(unique(srdat[, c("Stocknumber", "Name")])) %>% 
  left_join(scale_pi)
pred_lnSREP_pi <- pred_lnSREP_pi %>% left_join(unique(srdat[, c("Stocknumber", "Name")])) %>% 
  left_join(scale_pi)

pred_lSMSY_stream <- pred_lnSMSY_pi %>% filter(Param=="pred_lnSMSY") %>% left_join(stream) %>% 
  filter(lh == 0) %>% pull(Estimate) #Predicted lnSMSY from WA regression- stream - PlSMSYs
pred_lSMSY_ocean <- pred_lnSMSY_pi %>% filter(Param=="pred_lnSMSY") %>% left_join(stream) %>% 
  filter(lh == 1) %>% pull(Estimate) #Predicted lnSMSY from WA regression- ocean
obs_lSMSY_stream <- pred_lnSMSY_pi %>% filter(Param=="lnSMSY") %>% left_join(stream) %>% 
  filter( lh== 0) %>% pull(Estimate) # "observed" lnSMSY data output from SR models- stream
obs_lSMSY_ocean <- pred_lnSMSY_pi %>% filter(Param=="lnSMSY") %>% left_join(stream) %>% 
  filter(lh == 1) %>% pull(Estimate) # "observed" lnSMSY data output from SR models- ocean

pred_SREP_stream <- pred_lnSREP_pi %>% filter(Param=="pred_lnSREP") %>% left_join(stream) %>% 
  filter(lh == 0) %>% pull(Estimate) #Predicted lnSMSY from WA regression- stream
pred_SREP_ocean <- pred_lnSREP_pi %>% filter(Param=="pred_lnSREP") %>% left_join(stream) %>% 
  filter(lh == 1) %>% pull(Estimate) #Predicted lnSMSY from WA regression- ocean
obs_SREP_stream <- pred_lnSREP_pi %>% filter(Param=="lnSREP") %>% left_join(stream) %>% 
  filter(lh == 0) %>% pull(Estimate) # "observed" lnSMSY data output from SR models- stream
obs_SREP_ocean <- pred_lnSREP_pi %>% filter(Param=="lnSREP") %>% left_join(stream) %>% 
  filter(lh == 1) %>% pull(Estimate) # "observed" lnSMSY data output from SR models- ocean

wa_stream <- WA %>% left_join(stream) %>% filter(lh == 0) %>% pull(WA)
wa_ocean <- WA %>% left_join(stream) %>% filter(lh == 1) %>% pull(WA)
stocknames <- c(as.vector(wcvistocks$Stock), as.vector(InletlnWA$Inlet), as.vector(CUlnWA$CU))
target_SMSY_ocean <- data.frame()
target_SREP_ocean <- data.frame()

target_SMSY_stream <- data.frame()
target_SREP_stream <- data.frame()

condition_target <- cbind("ocean","stream") # choose if you want ocean, stream, or both

if ("ocean" %in% condition_target) {
  # Step 1
  target_SMSY_ocean <- all_pars %>% filter (Param %in% c("target_lnSMSY_ocean")) %>% add_column(Stock = stocknames)
  target_SREP_ocean <- all_pars %>% filter (Param %in% c("target_lnSREP_ocean")) %>% add_column(Stock = stocknames)
  target_SMSY_pull_ocean <- target_SMSY_ocean %>% pull(Estimate)
  target_SREP_pull_ocean <- target_SREP_ocean %>% pull(Estimate)
  # Step 2
  target_SMSY_pi_ocean <- PredInt(x = log(wa_ocean), y = obs_lSMSY_ocean, Predy = target_SMSY_pull_ocean, Newx = data$target_lnWA_ocean)
  target_SREP_pi_ocean <- PredInt(x = log(wa_ocean), y = obs_SREP_ocean, Predy = target_SREP_pull_ocean, Newx = data$target_lnWA_ocean)
  # Step 3
  target_SMSY_ocean <- target_SMSY_ocean %>% add_column(LL = exp(target_SMSY_pi_ocean$lwr), UL = exp(target_SMSY_pi_ocean$upr))
  target_SREP_ocean <- target_SREP_ocean %>% add_column(LL = exp(target_SREP_pi_ocean$lwr), UL = exp(target_SREP_pi_ocean$upr))
  # Step 4
  target_SMSY_ocean <- target_SMSY_ocean %>% mutate (Estimate = exp(Estimate)) %>% dplyr::select(-Std..Error, - Param) %>% 
    add_column(Param = "SMSY")
  target_SREP_ocean <- target_SREP_ocean %>% mutate (Estimate = exp(Estimate)) %>% dplyr::select(-Std..Error, - Param) %>% 
    add_column(Param = "SREP")
  # Step 5
  target_estimates_SMSY_ocean <- target_SMSY_ocean %>% mutate(Estimate = round(Estimate, 0), LL = round(LL,0), UL = round(UL,0))
  target_estimates_SREP_ocean <- target_SREP_ocean %>% mutate(Estimate = round(Estimate, 0), LL = round(LL,0), UL = round(UL,0))
}

# length_check_params <- all_pars %>% filter (Param %in% c("target_lnSMSY_ocean"))
# if (length(stocknames) == length(length_check_params$Estimate)) {
#   print("Lengths checked passed.")
# } else {
#   print("WARNING: The output and inputs are not the same length.")
# }

# if ("stream" %in% condition_target){
#   # Step 1
#   target_SMSY_stream <- all_pars %>% filter (Param %in% c("target_lnSMSY_stream")) %>% add_column(Stock = stocknames)
#   target_SREP_stream <- all_pars %>% filter (Param %in% c("target_lnSREP_stream")) %>% add_column(Stock = stocknames)
#   target_SMSY_pull_stream <- target_SMSY_stream %>% pull(Estimate)
#   target_SREP_pull_stream <- target_SREP_stream %>% pull(Estimate)
#   # Step 2
#   target_SMSY_pi_stream <- PredInt(x = log(wa_stream), y = obs_lSMSY_stream, Predy = target_SMSY_pull_stream, Newx = data$target_lnWA_stream)
#   target_SREP_pi_stream <- PredInt(x = log(wa_stream), y = obs_SREP_stream, Predy = target_SREP_pull_stream, Newx = data$target_lnWA_stream)
#   # Step 3
#   target_SMSY_stream <- target_SMSY_stream %>% add_column(LL = exp(target_SMSY_pi_stream$lwr), UL = exp(target_SMSY_pi_stream$upr))
#   target_SREP_stream <- target_SREP_stream %>% add_column(LL = exp(target_SREP_pi_stream$lwr), UL = exp(target_SREP_pi_stream$upr))
#   # Step 4
#   target_SMSY_stream <- target_SMSY_stream %>% mutate (Estimate = exp(Estimate)) %>% dplyr::select(-Std..Error, - Param) %>% 
#     add_column(Param = "SMSY")
#   target_SREP_stream <- target_SREP_stream %>% mutate (Estimate = exp(Estimate)) %>% dplyr::select(-Std..Error, - Param) %>% 
#     add_column(Param = "SREP")
#   # Step 5
#   target_estimates_SMSY_stream <- target_SMSY_stream %>% mutate(Estimate = round(Estimate, 0), LL = round(LL,0), UL = round(UL,0))
#   target_estimates_SREP_stream <- target_SREP_stream %>% mutate(Estimate = round(Estimate, 0), LL = round(LL,0), UL = round(UL,0))
# }

data_out_ocean <- target_estimates_SMSY_ocean %>% bind_rows(target_estimates_SREP_ocean)
# data_out_stream <- target_estimates_SMSY_stream %>% bind_rows(target_estimates_SREP_stream)

if(remove.EnhStocks) write.csv(data_out_ocean, here::here("DataOut/WCVI_target_ocean_noEnh.csv"))
if(!remove.EnhStocks) write.csv(data_out_ocean, here::here("DataOut/WCVI_target_ocean_wEnh.csv"))

# if(remove.EnhStocks) write.csv(data_out_stream, "DataOut/WCVI_target_stream_noEnh.csv")
# if(!remove.EnhStocks) write.csv(data_out_stream, "DataOut/WCVI_target_stream_wEnh.csv")
```

## Stage 2
- WCVILRPs_bootstrap - produce final SREP, SMSY, and SGen estimates for stocks

```{r bootstrap, include=TRUE}
# Bootstrap code loop - include
```

```{r bootstrap, include=TRUE}
# Bootstrap ouputs e.g. Table 9 in Case Study 2 Page 53:
  # Benchmarks and approximate 95% confidence limits for five inlets, not enhanced
# Is this the only major comparative outputs for the paper?
```

```{r bootstrap, include=TRUE}
# Plot: plotWCVI_timeseries (PlotFunctions.R)
# plotWCVI_timeseries(WCVIEsc=xx$WCVIEsc, remove.EnhStocks = TRUE, 
#                     prod="LifeStageModel")
```

## Stage 3
- Comparison of current outputs and previous outputs used in publication (LRP Paper)

## Conclusions
